---
title: "CIS361 Report"
author: "Nick Sheehan"
date: "5/5/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SUMMARY

  The problem I am trying to address is the equality of pay across the different genres of YouTube.  Is each genre generating the same kind of revenue for the highest viewed/subscribed channels?  If there is a difference, is it because of the nature of the genre, the demographic, or something else? These are the questions I will be asking myself and finding the answer for with this project.  This is important because equality of pay is an issue throughout any industry, but I think especially in YouTube as it becomes more of a known source of a way to make income.  I would like to see that there is relatively equal pay and no gross differences but these are important to point out if found.  That way people can start to think of ways to improve the inequality.
  
  There aren’t too many articles on my topic but the few I found had some interesting points. One being that the videos in overall more popular genres will get more views and in turn make more money.  Since YouTube pays mostly by CPM (Clicks per Mille), which basically means an amount for every thousand views the ads on their videos get.
Another good point that was brought up was video types.  Some video types tend to get more views than others, thus meaning more money. 

  A few research questions I am asking myself are: 
    - Which genres are the most viewed?
    - Does higher views have a direct impact on interactions? (Likes, Dislikes, and Comments)
    - Based off the two above, which genres are generating the most revenue
    
I believe there will be some pretty large differences in the salaries among the genres.  I also would expect to see genres tailored towards the younger demographic having the highest salaries.  I would also expect to see the genres with more family friendly content will generate more revenue compared to genres with 18+ material.


## DATA

First thing I needed to do was enable all the packages i will be using.
```{r}
#Enable Packages

library(tuber)
library(purrr)
library(stringr)
library(dplyr)
library(shiny)
library(rmarkdown)
library(ggplot2)
library(knitr)
```

Then I needed to source my data.  Since i was using information from YouTube, I needed to be able to hit their API's to collect data.  Luckily, they offer some public API's that you can access after setting up an account with Google Developers Console.  I was able to activate these APIs from my project and get my token using Auth 2.0.  Tuber offers the function yt_oauth that allows me to do this.
```{r}
#Authorization for Youtube APIs
client_id <- "871403720599-cjqncpljsnghb9las2sr0s87rdtm62ko.apps.googleusercontent.com"
client_secret <-  "UV1qXjK9TmVB9k6MzQLoJsjT"

yt_oauth(app_id = client_id,
         app_secret = client_secret,
         token = '')
```

Next, I needed to figure out the best way to collect the data from YouTube to fit my needs. What i decided to do, was to create a playlist for each main genre on YouTube and put the trending videos from each category in it.  Then I was able to use Tuber to pull my playlist, and strip out the video Ids.  I had to re-use this for each genre, and I could not place into a loop because I needed to save to different variables every iteration.
```{r}
#Get playlist Id for Music playlist
NickFBPlaylistId <- str_split(
  string = "https://www.youtube.com/playlist?list=PL1SoOwjbBbc-rh4v7ciKTtIcOyOpT11ov", 
  pattern = "=", 
  n = 2,
  simplify = TRUE)[ , 2]


#Put videos in playlist into data frame
NickFBPlaylist <- get_playlist_items(filter = 
                                              c(playlist_id = NickFBPlaylistId), 
                                              part = "contentDetails",
                                              max_results = 10)
#Save list of video ids
FB_ids <- base::as.vector(NickFBPlaylist$contentDetails.videoId)
```


#Function for get all stats on vids
get_all_stats <- function(id) {
  get_stats(video_id = id)
} 

#Get all stats for vid ids in that playlist
NickFBStats <- map_df(.x = FB_ids, .f = get_all_stats)

#get all details on vids
NickFBDetails <- lapply(FB_ids, get_video_details)
NickMusicDetails <- lapply(music_ids, get_video_details)
NickGamingDetails <- lapply(gaming_ids, get_video_details)
NickMoviesDetails <- lapply(movies_ids, get_video_details)

#Pull Id and Title from details

FBDetailsDF <- data.frame(id=NA, Title=NA)

for (p in 1:length(NickFBDetails)) {
  id <- NickFBDetails[[p]]$items[[1]]$id
  Title <- NickFBDetails[[p]]$items[[1]]$snippet$title
  
  FBdetail <- data_frame(id = id, Title = Title)
  FBDetailsDF <- rbind(FBdetail, FBDetailsDF)
}

#Merge details to stats data frame

NickMusicAllData <- merge(NickMusicStats,MusicDetailsDF,by = "id")
NickGamingAllData <- merge(NickGamingStats,GamingDetailsDF,by = "id")
NickMoviesAllData <- merge(NickMovieStats,MoviesDetailsDF,by = "id")
NickFBAllData <- merge(NickFBStats,FBDetailsDF,by = "id")

#Graph showing differences in views by main genres

options(scipen=999)

MusicGenreViewCount <- sum(as.numeric(NickMusicAllData$viewCount), na.rm = TRUE)
GamingGenreViewCount <- sum(as.numeric(NickGamingAllData$viewCount), na.rm = TRUE)
MoviesGenreViewCount <- sum(as.numeric(NickMoviesAllData$viewCount), na.rm = TRUE)
FBGenreViewCount <- sum(as.numeric(NickFBAllData$viewCount), na.rm = TRUE)

Genres <- c("Movies/Entertainment","Music","Gaming","Fashion/Beauty")
ViewCounts <- c(MoviesGenreViewCount,MusicGenreViewCount,GamingGenreViewCount,FBGenreViewCount)

BarGraphDF <- data.frame(Genres,ViewCounts)

ggplot(data=BarGraphDF, aes(x=Genres,y=ViewCounts))+
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=ViewCounts), vjust=1.6, color="white",size=3.5)+
  theme_minimal()

